R Markdown Features

### 2018-07-11 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

Rmarkdown requires specific formats of bibliographies. One of the most common one is `.bib`. A lot of people (including me) use Endnote to manage bibliographies and have no time getting used to other open source reference managers. Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` from EndNote.

>>>>

Rmarkdown requires specific formats of bibliographies. One of the most common one is `.bib`. A lot of people (including me) use Endnote to manage bibliographies. Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` files from EndNote.

However, you can't control the format of the **citation key** generated by Endnote. Having a well-structured format of citation key greatly enhance efficiency, which can be done by using **[Zotero](https://www.zotero.org/)** and its extension **[Better BibTeX](https://retorque.re/zotero-better-bibtex/)**. I strongly recommend using this approach, since the learning curve isn't steep and it only hurts once. The payoff is a long-term efficiency boost.
